\hypertarget{namespacepsYiiExtensions_1_1components}{
\section{psYiiExtensions::components Namespace Reference}
\label{namespacepsYiiExtensions_1_1components}\index{psYiiExtensions::components@{psYiiExtensions::components}}
}


\subsection{Detailed Description}
This file is part of the \hyperlink{namespacepsYiiExtensions}{psYiiExtensions} package.

Copyright (c) 2009-\/2011 Pogostick, LLC. \hyperlink{}{Pogostick, LLC.  \href{http://www.pogostick.com/licensing}{\tt http://www.pogostick.com/licensing} CPSFacebookConnect provides an interface to  \href{http://developers.facebook.com/connect.php}{\tt http://developers.facebook.com/connect.php} Facebook Connect\}   facebook   Jerry Ablan $<$\href{mailto:jablan@pogostick.com}{\tt jablan@pogostick.com}$>$  SVN:   v1.0.3    todo 4.  This file is part of the psYiiExtensions package.   Copyright (c) 2009-\/2011 Pogostick, LLC.  \href{http://www.pogostick.com}{\tt http://www.pogostick.com} Pogostick, LLC.  \href{http://www.pogostick.com/licensing}{\tt http://www.pogostick.com/licensing} CPSTwitterApi provides access to the  \href{http://apiwiki.twitter.com}{\tt http://apiwiki.twitter.com} Twitter API\}   twitter   Jerry Ablan $<$\href{mailto:jablan@pogostick.com}{\tt jablan@pogostick.com}$>$  SVN:   v1.0.3    todo 6.  This file is part of the psYiiExtensions package.   Copyright (c) 2009-\/2011 Pogostick, LLC.  \href{http://www.pogostick.com}{\tt http://www.pogostick.com} Pogostick, LLC.  \href{http://www.pogostick.com/licensing}{\tt http://www.pogostick.com/licensing} CPSYelpApi provides access to the Yelp Business Reviews API   yelp   Jerry Ablan $<$\href{mailto:jablan@pogostick.com}{\tt jablan@pogostick.com}$>$  SVN:   v1.0.4   }