\hypertarget{namespacesnowframe}{
\section{snowframe Namespace Reference}
\label{namespacesnowframe}\index{snowframe@{snowframe}}
}


\subsection{Detailed Description}
This file is part of the \hyperlink{classSnowFrame}{SnowFrame} package.

Copyright \copyright 2010 Pogostick, LLC \hyperlink{}{Pogostick, LLC.  \href{http://www.pogostick.com/licensing}{\tt http://www.pogostick.com/licensing} The base SnowFrame application   base   Jerry Ablan $<$\href{mailto:jablan@pogostick.com}{\tt jablan@pogostick.com}$>$  SVN:   v1.1.0    This file is part of SnowFrame(tm)   Copyright \copyright 2009-\/2010 Pogostick, LLC  \href{http://www.pogostick.com}{\tt http://www.pogostick.com} Pogostick, LLC.  \href{http://www.pogostick.com/licensing}{\tt http://www.pogostick.com/licensing}   base   Jerry Ablan $<$\href{mailto:jablan@pogostick.com}{\tt jablan@pogostick.com}$>$  SVN    The master SnowFrame include file   core  Jerry Ablan $<$\href{mailto:jablan@pogostick.com}{\tt jablan@pogostick.com}$>$  Copyright \copyright 2010 Pogostick, LLC  \$Id\$  Sonetrix.php  Copyright (c) 2010 Jerry Ablan $<$\href{mailto:jablan@pogostick.com}{\tt jablan@pogostick.com}$>$.  \href{http://www.pogostick.com}{\tt http://www.pogostick.com} Pogostick, LLC.  \href{http://www.pogostick.com/licensing}{\tt http://www.pogostick.com/licensing}  This file is part of Sonetrix by Pogostick, LLC.  We share the same open source ideals as does the jQuery team, and we love them so much we like to quote their license statement:  You may use our open source libraries under the terms of either the MIT License or the Gnu General Public License (GPL) Version 2.  The MIT License is recommended for most projects. It is simple and easy to understand, and it places almost no restrictions on what you can do with our code.  If the GPL suits your project better, you are also free to use our code under that license.  You don’t have to do anything special to choose one license or the other, and you don’t have to notify anyone which license you are using. Sonetrix PHP Client for Yii   components   Jerry Ablan $<$\href{mailto:jablan@pogostick.com}{\tt jablan@pogostick.com}$>$  SVN \$Id\$  v1.0.0    This file is part of the SnowFrame package.   Copyright \copyright 2010 Pogostick, LLC  \href{http://www.pogostick.com}{\tt http://www.pogostick.com} Pogostick, LLC.  \href{http://www.pogostick.com/licensing}{\tt http://www.pogostick.com/licensing} SnowFrame Helpers   helpers   Jerry Ablan $<$\href{mailto:jablan@pogostick.com}{\tt jablan@pogostick.com}$>$  SVN:   v1.1.0    This file is part of the SnowFrame package.   Copyright (c) 2009-\/2011 Pogostick, LLC.  \href{http://www.pogostick.com}{\tt http://www.pogostick.com} Pogostick, LLC.  \href{http://www.pogostick.com/licensing}{\tt http://www.pogostick.com/licensing}   helpers   Jerry Ablan $<$\href{mailto:jablan@pogostick.com}{\tt jablan@pogostick.com}$>$  SVN: \$Id\$  v1.1.0   }